Hydra Battles and Cie

### 2021-08-07 doc/chapter-powers.tex
resolve mistakes

\emph{From Module
\href{../theories/html/FirstSteps.html}{additions.FirstSteps}}

@@

In~\cite{BC04}, several exercices~\footnote{Exercises 9.8 (page 270), 9.10 (page 271), 9.15 (page 276), 9.17 (page 284), and 15.8 (page 418).}  
present ways to compute Fibonacci numbers, with the less number of recursive calls  as possible. Please note that these optimizations and the formal proof of their correctness are \emph{ad-hoc}, \emph{i.e.} exclusively written for the 
Fibonacci numbers.
In contrast, the optimizations we present in this document apply, in their vast majority, \emph{generic} techniques of efficient computation of powers in a monoid. 
This example of Fibonacci numbers has been developed with Yves Bertot, who wrote a first version with \texttt{SSreflect/Mathcomp}~\cite{MCB, SSR}.

@@

The relationship between \texttt{power} and \texttt{N\_bpow} can be considered
as a kind of \emph{refinement} as in the \texttt{B}-method~\cite{b-book}. Note
that the two representations of natural numbers and the function \texttt{N.to\_nat}
form a kind of  \emph{data refinement} \cite{Abrial:2010:MES:1855020, cohen:hal-01113453}.

>>>>

\emph{From Module
\href{../theories/html/additions.FirstSteps.html}{additions.FirstSteps}}

@@

In~\cite{BC04}, several exercices~\footnote{Exercises 9.8 (page 270), 9.10 (page 271), 9.15 (page 276), 9.17 (page 284), and 15.8 (page 418).}  
present ways to compute Fibonacci numbers, with the less number of recursive calls  as possible. Please note that these optimizations and the formal proof of their correctness are \emph{ad-hoc}, \emph{i.e.} exclusively written for the 
Fibonacci numbers.
In contrast, the optimizations we present in this document apply, in their vast majority, \emph{generic} techniques of efficient computation of powers in a monoid. 
This example of Fibonacci numbers has been developed with Yves Bertot, who wrote a first version with \texttt{SSreflect/Mathcomp}~\cite{MCB}.

@@

The relationship between \texttt{power} and \texttt{N\_bpow} can be considered
as a kind of \emph{refinement} as in the \texttt{B}-method~\cite{b-book}. Note
that the two representations of natural numbers and the function \texttt{N.to\_nat}
form a kind of  \emph{data refinement} \cite{Abrial:2010:MES:1855020, Cohen2013}.

### 2021-08-07 doc/part-hydras.tex
remove duplicate references
converting chapter 3 to alectryon (draft, completed)

In order to build an instance of \texttt{ON}, we define a comparison function,  and prove its correction.

@@

\begin{remark}
Finite ordinals are also formalized in MathComp~\cite{SSR}.  See also Adam Chlipala's \emph{CPDT}~\cite{chlipalacpdt2011} for a thorough study of the use of dependent types.  
\end{remark}

>>>>

In order to build an instance of \texttt{ON}, we define a comparison function,  and prove its correctiness.

@@

\begin{remark}
Finite ordinals are also formalized in MathComp~\cite{MCB}.  See also Adam Chlipala's \emph{CPDT}~\cite{chlipalacpdt2011} for a thorough study of the use of dependent types.  
\end{remark}
